A \textit{Proof} is a method for ascertaining (find (something) out for certain; make sure of) the \textbf{truth}. Examples of ways in which we ascertain proof:
\begin{enumerate}
    \item Experimentation and observation (bedrock of physics)
    \item Counterexamples
    \item Sampling (repeating a process a large number of times)
    \item Judge/Jury system
    \item Religion
    \item Word of boss (authority)
    \item Inner conviction
\end{enumerate}

\subsection{Mathematical Proof}
A \textit{Mathematical Proof} is a verification of a \textbf{Proposition} by a chain of \textbf{logical deductions} from a set of \textbf{axioms}.

\subsection{Proposition}
A Proposition is a statement that is either true or false. Examples:
\begin{itemize}
    \item $2+3=5$
    \item $\forall n\in  \mathbb{N}, n^2+n+41$ is a prime number.
\end{itemize}

\subsubsection{Predicate}
$$
    \forall n \in \mathbb{N}, \underbrace{n^2 + n + 41}_{\text{Predicate}}
$$
A Predicate is a Proposition whose truth is determined by the values of its variables.

In order to determine if this Proposition is true, we need to make sure that this Predicate is true for every Natural Number $\mathbb{N}$. Lets verify the Predicate by plugging in some values of Natural Numbers. The predicate if false, even though it worked for the first 40 numbers.

\[
    \begin{array}{|c|c|c|}
        \hline
        n      & n^2 + n + 41 & \text{Prime} \\
        \hline
        0      & 41           & \checkmark   \\
        1      & 43           & \checkmark   \\
        2      & 47           & \checkmark   \\
        3      & 53           & \checkmark   \\
        \vdots & \vdots       & \vdots       \\
        20     & 461          & \checkmark   \\
        \vdots & \vdots       & \vdots       \\
        39     & 1601         & \checkmark   \\
        40     & 1681=41^2    & \times       \\
        41     & .            & \times       \\
        \hline
    \end{array}
\]

\subsection{Euler's Theorem}

\begin{example}
    $a^4 + b^4 + c^4 = d^4$ has no positive integer solutions.
\end{example}

This proposition was unsolved for centuries. It was conjectured to be true by Euler in 1769. It was disproved recently using very big numbers. Hence the correct Proposition would be :

$$
    \exists \quad a, b, c, d \in \mathbb{N}^+, \quad \underbrace{a^4 + b^4 + c^4 = d^4}_{\text{Predicate}}
$$
We care about such these proof problems because they involve \textit{Factoring large integers}. It is a way to break crypto systems like RSA which are used for everything we do electronically today.

\begin{example}
    The regions in any map can be coloured in 4 colours such that adjacent regions have different colours.
\end{example}